Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-14 paper/paper.qmd
Finished data section and midway through sampling approach in appendix

The Federal Bureau of Investigation (FBI) has a program called the Uniform Crime Reporting (UCR) Program to generate statistics for the public [@citeFBIinfo]. The FBI originally had a system under the UCR called Summary Reporting System (SRS), which obtained details about different crimes taking place from law enforcement agencies nationwide such as victim information [@citeFBIinfo]. However, the SRS was replaced with a new system called the National Incident-Based Reporting System (NIBR) in 2021 that obtained more details about various crimes [@citeFBIinfo]. For The Los Angeles Police Department, after a homicide case occurs, the investigating team handwrites information into physical crime reports with details like the type of crime, the premise the crime occured at, and the age and ethnicity of the victim [@citeLApolice]. The crime reports are then transcribed into a digital format and then sent to the SRS monthly [@citeLApolice]. After a homicide occurs in Chicago, The Chicago Police Department uses a system called the Chicago Police Department's CLEAR (Citizen Law Enforcement Analysis and Reporting) system to report on details such as the victim, if an arrest was made or not, and the location the crime took [@citeChicagoPolice]. This information is then reported to the FBI under the UCR program.

Reporters from the Washington Post then obtained the data from the FBI specifically on homicides from 50 large US cities from 2007 to 2010, which can be access through the UCR publications page on the FBI website [@datahomicides]. They also obtain data about homicide counts and closure rates through papers and compare these values with the ones from the FBI dataset for accuracy [@datahomicides]. The Washington Post would also use public records like medical examiner reports, death certificates, and court records, to fill in any missing information since some departments only report partial information to the FBI [@datahomicides]. The Washington Post defined cases to be closed without arrest when they are reported by the police as "exceptionally cleared" where there is evidence of who the perpetrator is but an arrest is not possible because of reason like they has died [@datahomicides]. They also define cases to be closed by arrest if the police reported it to be and other cases are defined to be open/no arrest [@datahomicides].

@@

## Overview and Evaluation of The Washington Post’s Methodology {#sec-data-evalulation}
- TODO: Make sure to link evaluation to literature

@@

### Sampling Approach
The population @datahomicides were interested in were homicide victims in the US [@citetellingstories]. As defined by @citetellingstories, their sampling frame is homicide victims from the 50 largest US cities. However

- what is the population, frame, and sample;
- how is the sample recruited;
- what sampling approach is taken, and what are some of the trade-offs of this; 
- how is non-response handled; - They marked it as "Unknown" or left the field blank.

>>>>

The Federal Bureau of Investigation (FBI) has a program called the Uniform Crime Reporting (UCR) Program to generate statistics for the public [@citeFBIinfo]. The FBI originally had a system under the UCR called Summary Reporting System (SRS), which obtained details about different crimes taking place from law enforcement agencies nationwide such as victim information [@citeFBIinfo]. However, the SRS was replaced with a new system called the National Incident-Based Reporting System (NIBR) in 2021 that obtained more details about various crimes [@citeFBIinfo]. For The Los Angeles Police Department, after a homicide case occurs, the investigating team handwrites information into physical crime reports with details like the type of crime, the premise the crime occured at, and the age and ethnicity of the victim [@citeLApolice]. The crime reports are then transcribed into a digital format and then sent to the SRS monthly [@citeLApolice]. After a homicide occurs in Chicago, The Chicago Police Department uses a system called the Chicago Police Department's CLEAR (Citizen Law Enforcement Analysis and Reporting) system to report on details such as the victim, if an arrest was made or not, and the location the crime took [@citeChicagoPolice]. This information is then reported to the FBI monthly under the UCR program [@citeChicagoPolice].

Reporters from the Washington Post then obtained the data from the FBI specifically on homicides from 50 largest US cities from 2007 to 2017, which can be access through the UCR publications page on the FBI website [@datahomicides]. They selected the 50 largest cities based the size of the city in 2012 [@datahomicides]. They also obtain data about homicide counts and closure rates through papers and compare these values with the ones from the FBI dataset for accuracy [@datahomicides]. The Washington Post would also use public records like medical examiner reports, death certificates, and court records, to fill in any missing information since some departments only report partial information to the FBI [@datahomicides]. The Washington Post defined cases to be closed without arrest when they are reported by the police as "exceptionally cleared" where there is evidence of who the perpetrator is but an arrest is not possible because of reason like they has died [@datahomicides]. They also define cases to be closed by arrest if the police reported it to be and other cases are defined to be open/no arrest [@datahomicides].

@@

## Overview and Evaluation of The Washington Post’s Methodology {#sec-data-evalulation}

@@

### Sampling Approach
The population @datahomicides were interested in were homicide victims in the US [@citetellingstories]. As defined by @citetellingstories, their sampling frame are homicide victims from 2007 to 2017 from the 50 largest US cities [@datahomicides]. However, the sample @datahomicides had contains the homicide victims from 2007 to 2017 from the 50 largest US cities they can gather data on. How @datahomicides determine the 50 largest cities was based on the size of the city as of 2012 who reported homicides to the FBI. They selected 2012 since it was the middle year in their sampling [@datahomicides]. To obtain the sample, @datahomicides started by gathering homicide data collected by the FBI that can be accessed through the UCR publications page on the FBI website from 2007 to 2012 of the 50 largest cities [@citeFBIinfo].

The UCR program originally had a system until 2021 called the Summary Reporting System (SRS), which obtained details about different crimes such as victim information taking place that are reported by law enforcement agencies nationwide [@citeFBIinfo]. @datahomicides obtained their data collected through the Summary Reporting System (SRS). As noted in @sec-data, police agencies have different methods of collecting homicide crime data. The Chicago Police Department has a digital system called CLEAR (Citizen Law Enforcement Analysis and Reporting), where they would enter in the victim's details, the location of the crime, and if an arrest was made or not once a homicide is reported [@citeChicagoPolice]. This information is then reported to the FBI through the UCR program monthly [@citeChicagoPolice]. On the other hand, The Los Angeles Police Department would initially handwrite a physical report about the crime with details such as the type of crime, the premise the crime occured at, and the age and ethnicity of the victim [@citeLApolice]. On a monthly basis, the information will be transcribed into a digital format to be sent to the FBI  [@citeLApolice].

Since the FBI collect data on different crimes other than homicide, @datahomicides used the UCR's definition of homicides, which is defined to be "murder and non-negligent manslaughter but exclude suicides, accidents, justifiable homicides and deaths caused by negligence", to filter for only homicides [@datahomicides]. However, not all police departments give all information about homicides leading to non-response bias [@citetellingstories]. To address this, they

- what is the population, frame, and sample;
- how is the sample recruited;
- how is non-response handled; - They marked it as "Unknown" or left the field blank. 
- what sampling approach is taken, and what are some of the trade-offs of this;
